What Happened to The Birth Rate?

### 2022-02-28 outputs/paper/paper.Rmd
pull

We do observe declinations of world-wide birth rate despite of the impact level from recession. From the economic perspective, the countries who are least affected tend to have a stronger resistance to recession but not necessarily developed countries. While the most affected countries are mostly developing countries, they experienced a more significant plummet as percentage. It is also intriguing that the long-term births per 1000 people tend to converge to 10 for all countries mentioned above. However, the countries have higher resistance tend to delay the convergence which may derived from stronger economic status. Overall, the Great Recession was a turning point not only for the U.S. but also the whole world in the context of birth rate. The Great Recession may not be the direct cause of the world-wide declination in birth rates but it indeed provided an opportunity and provoked the desire for people to reconsider personal priorities with changed perspective of the society.

@@

Figure \@ref(fig:fig-lgbt-trend-by-year) shows the trend of LGBT population percentage in total population.
There is an obvious increasing trend (i.e. higher percentage of the US population are becoming LGBT). 
Figure \@ref(fig:fig-lgbt-by-generation) shows the percentage of LGBT population trend in different generations.
We can also see an increasing trend of LGBT population percentage (younger generations are more and more likely to become LGBT).
This provide more evidence that cohort effects may contribute to the delines of birth rate in the US in recent years.

\newpage

# References

>>>>

@@

Figure \@ref(fig:fig-lgbt-trend-by-year) shows the trend of LGBT population percentage in total population.
There is an obvious increasing trend (i.e. higher percentage of the US population are becoming LGBT). 
Figure \@ref(fig:fig-lgbt-by-generation) shows the percentage of LGBT population trend in different generations.
We can also see an increasing trend of LGBT population percentage (younger generations are more and more likely to become LGBT).
This provide more evidence that cohort effects may contribute to the declines of birth rate in the US in recent years.

# Discussion

## Global Comparison

We do observe declination of world-wide birth rate despite of the impact level from recession. From the economic perspective, the countries who are least affected tend to have a stronger resistance to recession but not necessarily developed countries. While the most affected countries are mostly developing countries, they experienced a more significant plummet as percentage. It is also intriguing that the long-term births per 1000 people tend to converge to 10 for all countries mentioned above. However, the countries have higher resistance tend to delay the convergence which may derived from stronger economic status. Overall, the Great Recession was a turning point not only for the U.S. but also the whole world in the context of birth rate. The Great Recession may not be the direct cause of the world-wide declination in birth rates but it indeed provided an opportunity and provoked the desire for people to reconsider personal priorities with changed perspective of the society.

\newpage
# References
